working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-02-25 Manuscript_draft/Manuscript_draft.Rmd
changes methods

In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits (Euclidean distances). Heterospecific pollen effect was considered as the subtraction of seed production by hand cross pollination minus seed production of the different heterospecific pollen treatments. To find a model with the best explanatory traits we used the function **bioenv** from R. We also conducted Mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits. Moreover, we explored also the correlation between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect and the explanatory variable the different traits.

We conducted mantel test to check for correlations between heterospecific pollen effect and phylogenetic distance. Due to improvents in statistical power we used the square root of the phylogenetic distance (Letten & Cornwell 2014). Two different phylogenetic distances were used from two kinds of markers: 1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase (RBCL). The sequences were obtained from GenBank (https://www.ncbi.nlm.nih.gov/genbank/, accessed 20 Oct. 2018). The sequences were aligned with clustal omega and the pairwise evolutive distances were calculated with MEGA7.

>>>>

In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits (Euclidean distances). Heterospecific pollen effect was obtain through the subtraction of seed production by hand cross pollination minus seed production of the different heterospecific pollen treatments. To find a model with the best explanatory traits we used the function **bioenv** from R. We also conducted Mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits. Moreover, we explored also the correlation between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect and the explanatory variable the different traits.

We conducted mantel test to check for correlations between heterospecific pollen effect and phylogenetic distance. Due to improvents in statistical power we used the square root of the phylogenetic distance (Letten & Cornwell 2014). Two different phylogenetic distances were used from two kinds of markers: 1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase (RBCL). The sequences were obtained from GenBank (https://www.ncbi.nlm.nih.gov/genbank/, accessed 20 Oct. 2018). The sequences were aligned with clustal omega and the pairwise evolutive distances calculated with MEGA7.

### 2019-02-25 Manuscript_draft/Manuscript_draft.tex
changes methods

In order to test the relative effect of traits on seed production with
foreign pollen we performed Mantel test between the assymetrical matrix
of heterospecific pollen effect (10 by 10 matrix) with the different
distance matrices of traits (Euclidean distances). Heterospecific pollen
effect was considered as the subtraction of seed production by hand
cross pollination minus seed production of the different heterospecific
pollen treatments. To find a model with the best explanatory traits we
used the function \textbf{bioenv} from R. We also conducted Mantel test
between the matrix of heterospecific pollen effect and the distance
matrix from all the traits. Moreover, we explored also the correlation
between traits and heterospecific pollen effect through generalized
mixed models where the response variable was heterospecific pollen
effect and the explanatory variable the different traits.

We conducted mantel test to check for correlations between
heterospecific pollen effect and phylogenetic distance. Due to
improvents in statistical power we used the square root of the
phylogenetic distance (Letten \& Cornwell 2014). Two different
phylogenetic distances were used from two kinds of markers: 1) Internal
transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase
(RBCL). The sequences were obtained from GenBank
(\url{https://www.ncbi.nlm.nih.gov/genbank/}, accessed 20 Oct. 2018).
The sequences were aligned with clustal omega and the pairwise evolutive
distances were calculated with MEGA7.

>>>>

In order to test the relative effect of traits on seed production with
foreign pollen we performed Mantel test between the assymetrical matrix
of heterospecific pollen effect (10 by 10 matrix) with the different
distance matrices of traits (Euclidean distances). Heterospecific pollen
effect was obtain through the subtraction of seed production by hand
cross pollination minus seed production of the different heterospecific
pollen treatments. To find a model with the best explanatory traits we
used the function \textbf{bioenv} from R. We also conducted Mantel test
between the matrix of heterospecific pollen effect and the distance
matrix from all the traits. Moreover, we explored also the correlation
between traits and heterospecific pollen effect through generalized
mixed models where the response variable was heterospecific pollen
effect and the explanatory variable the different traits.

We conducted mantel test to check for correlations between
heterospecific pollen effect and phylogenetic distance. Due to
improvents in statistical power we used the square root of the
phylogenetic distance (Letten \& Cornwell 2014). Two different
phylogenetic distances were used from two kinds of markers: 1) Internal
transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase
(RBCL). The sequences were obtained from GenBank
(\url{https://www.ncbi.nlm.nih.gov/genbank/}, accessed 20 Oct. 2018).
The sequences were aligned with clustal omega and the pairwise evolutive
distances calculated with MEGA7.
